Spá: a web-based viewer for text mining in Evidence Based Medicine

### 2014-04-15 documentation/paper.tex
Documentation fixes

To aid the process of systematic reviewing we made a web-based tool that allows the visualization of annotations within a PDF documents, and meta-information alongside it.
The vision is to have a system to allow for semi-automated (machine assisted) screening, data extraction and data summarization.

\subsection{Machine Learning Strategies}

\begin{itemize}
\item Basically show that we're using state of the art
\item Briefly talk about cochrane DB / distant supervision
\item KDD stuff (briefly)
\item Multi-task stuff!
\end{itemize}

@@

However, we believe the tool to be useful for a much wider range of text mining and machine learning applications.
To increase the generality of the tool work is being done to support a pluggable system for processing topologies, allowing developers to quickly plug in new systems.
Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.

>>>>

To aid the process of systematic reviewing we made a web-based tool that allows the visualization of annotations within a PDF documents, and meta-information alongside it.

\subsection{Machine Learning Strategies}
When doing risk of bias assessment one wishes to \highlight{todo}

% \begin{itemize}
% \item Basically show that we're using state of the art
% \item Briefly talk about cochrane DB / distant supervision
% \item KDD stuff (briefly)
% \item Multi-task stuff!
% \end{itemize}

@@

However, we believe the tool to be useful for a much wider range of text mining and machine learning applications.
To increase the generality of the tool work is being done to support a pluggable system for processing topologies, allowing developers to quickly plug in new systems.
Furthermore, work is being done on allowing users to save selected annotations, possibly embedded within the document itself, for sharing and off-line use.
The ultimate vision is to have a extensible system for semi-automated (machine assisted) screening, data extraction and data summarization.
